Imputation of Incomplete Multilevel Data with R

### 2023-12-22 Manuscript/manuscript.qmd
Render manuscript

```{r}
#| label: setup
#| echo: false
#| warning: false
#| message: false
library(knitr)
library(ggplot2)
source("../docs/utils.R")
source("../docs/tables.R")
```

>>>>

```{r}
#| label: setup
#| echo: false
#| warning: false
#| message: false
set.seed(1)
library(knitr)
library(ggplot2)
source("../Manuscript/utils.R")
source("../Manuscript/tables.R")
```

### 2023-12-22 Manuscript/manuscript.tex
Render manuscript

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

@@

\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Imputation of Incomplete Multilevel Data with R},
  pdfauthor={Hanne I. Oberman; Johanna Muñoz; Valentijn M.T. de Jong; Gerko Vink; Thomas P.A. Debray},
  pdfkeywords={missing data, multilevel, clustering, mice, R},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\hypertarget{sec-intro}{%
\section{Introduction: Clustering and incomplete data}\label{sec-intro}}

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, arc=.35mm, rightrule=.15mm, breakable, opacityback=0, bottomrule=.15mm, colback=white, leftrule=.75mm, left=2mm]

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0924}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0924}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0924}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2017}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1008}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
estimate1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
estimate2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
statistic
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
p.value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
conf.low
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
conf.high
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
method
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
alternative
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-0.2599581 & 14.15278 & 14.41274 & -0.8731291 & 0.3827095 & 1796.115 &
-0.8438947 & 0.3239786 & Welch Two Sample t-test & two.sided \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1558}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1169}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1299}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1039}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1039}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2338}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0779}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0779}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Std.Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
t.value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
df
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
P(\textgreater\textbar t\textbar)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
RIV
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
FMI
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
(Intercept) & 3.599 & 0.181 & 19.924 & 246.857 & 0 & 0.146 & 0.134 \\
texp & 0.092 & 0.012 & 7.760 & 107.369 & 0 & 0.239 & 0.208 \\
sex & 0.852 & 0.039 & 21.592 & 27.501 & 0 & 0.616 & 0.422 \\
\end{longtable}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
& Estimate \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept\textasciitilde\textasciitilde Intercept\textbar school &
0.470 \\
Residual\textasciitilde\textasciitilde Residual & 0.462 \\
ICC\textbar school & 0.504 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1605}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1111}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1235}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0988}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1358}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2222}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0741}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0741}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Std.Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
t.value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
df
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
P(\textgreater\textbar t\textbar)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
RIV
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
FMI
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
(Intercept) & -1.892 & 0.333 & -5.682 & 11445.455 & 0.000 & 0.019 &
0.019 \\
type & -0.346 & 0.178 & -1.948 & 686356.768 & 0.051 & 0.002 & 0.002 \\
age & 0.032 & 0.002 & 19.564 & 2418.910 & 0.000 & 0.042 & 0.041 \\
motor\_score2 & -0.575 & 0.070 & -8.226 & 71295.018 & 0.000 & 0.008 &
0.008 \\
motor\_score3 & -0.891 & 0.072 & -12.440 & 66712.189 & 0.000 & 0.008 &
0.008 \\
motor\_score4 & -1.276 & 0.074 & -17.305 & 18426.087 & 0.000 & 0.015 &
0.015 \\
pupil2 & 1.315 & 0.068 & 19.339 & 110.826 & 0.000 & 0.235 & 0.204 \\
pupil3 & 0.657 & 0.075 & 8.745 & 423.463 & 0.000 & 0.108 & 0.101 \\
ct2 & 0.747 & 0.084 & 8.884 & 41.781 & 0.000 & 0.448 & 0.340 \\
ct3 & 0.766 & 0.090 & 8.535 & 12.103 & 0.000 & 1.352 & 0.631 \\
\end{longtable}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
& Estimate \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept\textasciitilde\textasciitilde Intercept\textbar name &
0.082 \\
\end{longtable}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
& Estimate \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept\textasciitilde\textasciitilde Intercept\textbar Cluster &
19.862 \\
Age\textasciitilde\textasciitilde Age\textbar Cluster & 0.002 \\
Intercept\textasciitilde\textasciitilde Age\textbar Cluster & -0.067 \\
Residual\textasciitilde\textasciitilde Residual & 26.010 \\
ICC\textbar Cluster & 0.395 \\
\end{longtable}

@@

\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  16.26   70.95   85.21   86.14  100.14  190.95 
\end{verbatim}

@@

\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  28.35   71.51   85.07   85.35   98.90  134.61 
\end{verbatim}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
& Estimate \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept\textasciitilde\textasciitilde Intercept\textbar Cluster &
19.111 \\
Age\textasciitilde\textasciitilde Age\textbar Cluster & 0.001 \\
Intercept\textasciitilde\textasciitilde Age\textbar Cluster & -0.046 \\
Residual\textasciitilde\textasciitilde Residual & 30.071 \\
ICC\textbar Cluster & 0.372 \\
\end{longtable}

@@

\renewcommand{\bibsection}{}
\bibliography{bibliography.bib}

@@

>>>>

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Imputation of Incomplete Multilevel Data with R},
  pdfauthor={Hanne I. Oberman; Johanna Muñoz; Valentijn M.T. de Jong; Gerko Vink; Thomas P.A. Debray},
  pdfkeywords={missing data, multilevel, clustering, mice, R},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, breakable, sharp corners, interior hidden]}{\end{tcolorbox}}\fi

\hypertarget{sec-intro}{%
\section{Introduction: Clustering and incomplete data}\label{sec-intro}}

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, toprule=.15mm, arc=.35mm, bottomrule=.15mm, leftrule=.75mm, colframe=quarto-callout-color-frame, opacityback=0, colback=white, rightrule=.15mm, left=2mm]

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0924}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0924}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0924}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0840}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2017}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1008}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedleft
estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
estimate1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
estimate2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
statistic
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
p.value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
conf.low
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
conf.high
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
method
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
alternative
\end{minipage} \\
\midrule()
\endhead
-0.2599581 & 14.15278 & 14.41274 & -0.8731291 & 0.3827095 & 1796.115 &
-0.8438947 & 0.3239786 & Welch Two Sample t-test & two.sided \\
\bottomrule()
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1558}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1169}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1299}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1039}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1039}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2338}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0779}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0779}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Std.Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
t.value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
df
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
P(\textgreater\textbar t\textbar)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
RIV
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
FMI
\end{minipage} \\
\midrule()
\endhead
(Intercept) & 3.599 & 0.181 & 19.924 & 246.857 & 0 & 0.146 & 0.134 \\
texp & 0.092 & 0.012 & 7.760 & 107.369 & 0 & 0.239 & 0.208 \\
sex & 0.852 & 0.039 & 21.592 & 27.501 & 0 & 0.616 & 0.422 \\
\bottomrule()
\end{longtable}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule()
& Estimate \\
\midrule()
\endhead
Intercept\textasciitilde\textasciitilde Intercept\textbar school &
0.470 \\
Residual\textasciitilde\textasciitilde Residual & 0.462 \\
ICC\textbar school & 0.504 \\
\bottomrule()
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1605}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1111}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1235}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0988}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1358}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2222}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0741}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0741}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Std.Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
t.value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
df
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
P(\textgreater\textbar t\textbar)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
RIV
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
FMI
\end{minipage} \\
\midrule()
\endhead
(Intercept) & -1.892 & 0.333 & -5.682 & 11445.455 & 0.000 & 0.019 &
0.019 \\
type & -0.346 & 0.178 & -1.948 & 686356.768 & 0.051 & 0.002 & 0.002 \\
age & 0.032 & 0.002 & 19.564 & 2418.910 & 0.000 & 0.042 & 0.041 \\
motor\_score2 & -0.575 & 0.070 & -8.226 & 71295.018 & 0.000 & 0.008 &
0.008 \\
motor\_score3 & -0.891 & 0.072 & -12.440 & 66712.189 & 0.000 & 0.008 &
0.008 \\
motor\_score4 & -1.276 & 0.074 & -17.305 & 18426.087 & 0.000 & 0.015 &
0.015 \\
pupil2 & 1.315 & 0.068 & 19.339 & 110.826 & 0.000 & 0.235 & 0.204 \\
pupil3 & 0.657 & 0.075 & 8.745 & 423.463 & 0.000 & 0.108 & 0.101 \\
ct2 & 0.747 & 0.084 & 8.884 & 41.781 & 0.000 & 0.448 & 0.340 \\
ct3 & 0.766 & 0.090 & 8.535 & 12.103 & 0.000 & 1.352 & 0.631 \\
\bottomrule()
\end{longtable}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule()
& Estimate \\
\midrule()
\endhead
Intercept\textasciitilde\textasciitilde Intercept\textbar name &
0.082 \\
\bottomrule()
\end{longtable}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule()
& Estimate \\
\midrule()
\endhead
Intercept\textasciitilde\textasciitilde Intercept\textbar Cluster &
19.805 \\
Age\textasciitilde\textasciitilde Age\textbar Cluster & 0.003 \\
Intercept\textasciitilde\textasciitilde Age\textbar Cluster & -0.069 \\
Residual\textasciitilde\textasciitilde Residual & 26.010 \\
ICC\textbar Cluster & 0.394 \\
\bottomrule()
\end{longtable}

@@

\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  16.31   72.14   86.97   87.68  102.43  190.44 
\end{verbatim}

@@

\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  28.35   71.87   85.58   86.51  100.15  134.61 
\end{verbatim}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule()
& Estimate \\
\midrule()
\endhead
Intercept\textasciitilde\textasciitilde Intercept\textbar Cluster &
26.114 \\
Age\textasciitilde\textasciitilde Age\textbar Cluster & 0.002 \\
Intercept\textasciitilde\textasciitilde Age\textbar Cluster & -0.088 \\
Residual\textasciitilde\textasciitilde Residual & 29.741 \\
ICC\textbar Cluster & 0.431 \\
\bottomrule()
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

@@

  \bibliography{bibliography.bib}
